### 2020-09-07 README.Rmd

Install the CRAN version:
```{r, eval=FALSE}
install.packages("robvis")
```

Alternatively, the development version can be installed using:

@@

@@

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
ggplot2::ggsave(
          "man/figures/rob2trafficlight.png",
          plot = trafficlight_rob,
          device = "png",
          width = 6,
          height = 9,
          units = "in",
          dpi = 800, 
          limitsize = FALSE)
```
<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>

### Other functions
#### rob_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). We expect this list to be updated in the near future to include tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

    rob_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"
    [1] "ROB1"

@@

And to define your own colour scheme:
```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000"))
summary_rob
```

@@

>>>>

Install the development version which contains new functionality and a range of bug fixes:

@@

If you wish to use the older CRAN version of the package, use the following command:

```{r, eval=FALSE}
install.packages("robvis")
```

@@

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
rob_save(trafficlight_rob,"man/figures/rob2trafficlight.png")
```
<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>

### Other functions

#### rob_save()
Pass the `robvis` to this function, along with a destination file, to save your risk-of-bias plots using sensible defaults.

```{r, eval = FALSE}
rob_save(trafficlight_rob, "rob_fig.png")
```

#### rob_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). We expect this list to be updated in the near future to include tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

```{r}
rob_tools()
```

@@

And to define your own colour scheme:
```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000","#d16684"))
summary_rob
```

@@

See more [here](https://scholar.google.com/scholar?cites=12564214960529060925&as_sdt=2005&sciodt=0,5&hl=en).
